---
title: "p8105_hw1_pika1218"
author: "pika"
date: "1/18/2022"
output: github_document
---
## load library

```{r}
library(tidyverse)
```

## Problem 1
Create a date frame. 
```{r}
problem1_df = tibble(
  vec_numeric = rnorm(10),
  vec_logical = vec_numeric > 0,
  vec_character = c("a", "b" , "c", "d", "e", "f", "g", "h", "i", "j"),
  vec_factor = factor(c("infant", "infant", "toddler", "infant", "adult", "infant", "adult", "toddler", "infant", "toddler"))
  
)
```

take the mean of each variable in the `problem_df` 

```{r}
mean(pull(problem1_df, vec_numeric))
mean(pull(problem1_df, vec_logical))
mean(pull(problem1_df, vec_character))
mean(pull(problem1_df, vec_factor))

```

The vec_numeric and vec_ligical can calculate mean number. The vec_character and vec_factor doesn't has mean number. 

```{r}
mean(as.numeric(pull(problem1_df, vec_numeric)))
mean(as.numeric(pull(problem1_df, vec_logical)))
mean(as.numeric(pull(problem1_df, vec_factor)))
mean(as.numeric(pull(problem1_df, vec_factor)))
```


# Problem2
```{r}
data("penguins", package = "palmerpenguins")
```
In the dataset of penguins, the important variable is Species which is penguins name. 
This dataset including `r nrow(penguins)` rows, and `r ncol(penguins)` columns.
The mean is `r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)`.

```{r}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
ggsave("p8105_hw1_pika1218.pdf")



```





